Blowship - Anonymous Communication via a Central Server

### 2014-03-09 paper.tex
Fleshy flesh

\documentclass{paper}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage[margin=1.0in]{geometry}

\title{Blowship}
\author[*]{John Carlyle}
\author[**]{Morgan McDermott}
\affil[*]{University of fighitng bears}
\affil[**]{University of sillypants}

\begin{document}
\maketitle
\twocolumn
\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
\section{Previous Work}
There has been a plethora of original work and refinement in the area of anonymous internet communication. Broadly categorized, these include:
\begin{enumerate}
  \item Mixes \cite{chaum-mix} 
  \item Onion routing \cite{onion-discex00}
  \item Freedom (wtf) [z]
\end{enumerate}
\section{Privacy Goals}
  The goal of this system is to provide an in-browser method for communicating securely between parties without massive latency or communication overhead. We attempt to satisfy these requirements assuming the intermediate server may be compromised. By communicating securely we mean specifically (using terminology from \textbf{[6]}):
  \\\\\textbf{Communication Privacy}. Any party Eve cannot read the contents of intercepted messages sent between any two parties Alice and Bob. 
  \\\textbf{Participant Privacy}. This is also called \textbf{Unobservability} and \textbf{Untraceability}. Any party Eve, cannot determine with probability $p > \epsilon$ that the two are communicating, given any $\epsilon$ chosen by Alice and Bob (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants). The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
  \\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
\section{PSP}
In this section we introduce
$P2(S2P2)^nP$, or PSP for short. PSP is an alternative to P2P protocols in which peers communicate with eachother through an alternating chain of peer-server and server-peer communications.

\begin{figure}[ht]
  \includegraphics[width=230px]{PSP.png}
  \caption{A simple PSP communication chain}
\end{figure}

@@

In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[TODO]]], as well (as we will discuss) by reordering and batching messages. 
\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{enumerate}
  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
\end{enumerate}
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
Let $P_{AB}$ be the probability that Alice is talking to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ... P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{P_1 ... P_n\}$ talked to Bob.
\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $P_1 ... P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.

@@

If we assume that there is not a Palace, then Alice needs only choose $n = O(log(N))$, and then Surge can only tell that $P_{AB} = 2^{-O(log(N))} \approx 1/N $. If every node sends 2 messages at once, and her message passes through $O(log(N))$ nodes, then there are $O(2^n)$ possible routes her message could have taken and hopefully $O(2^n)$ possible destinations. The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.

In this way Surge gains no information about $P_{AB}$. If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, which is still reasonable.

\paragraph{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$. If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$. The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.

@@

\paragraph{The Dictatorship.}
Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace.

This is still a problem.
\subsection{Peers as Mixes}
As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities. Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions. 
A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages. Common attacks are variants of the $n - 1$ or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.

@@

It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack. However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.

\bibliography{paper.bib}
\bibliographystyle{plain}
\end{document}

>>>>

\documentclass{paper}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{cite}
\usepackage{relsize}
\usepackage[margin=1.0in]{geometry}

\title{Blowship - Anonymous Communication via a Central Server}
\author[*]{John Carlyle}
\author[**]{Morgan McDermott}
\affil[*]{University of fighitng bears}
\affil[**]{University of sillypants}

\begin{document}
\maketitle
\twocolumn

\section*{Abstract} 
  Many systems have been developed that preserve the anonymity of the sender and receiver of data. These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.

In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized p2p protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
\section{Introduction}

\section{Previous Work}
\paragraph{Mixes.} Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies. Mixes have seen wide use since Chaum first introduced them in his 1981 paper \cite{chaum-mix}. They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email. [TODO: more explanation]
\paragraph{Onion Routing.} \cite{onion-discex00}
\paragraph{Nym systems.} Pseudonymous message delivery systems enable users to send messages from a \textit{nym} (pseudonym) that cannot be traced back to their true identity. Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we are attempting to develop in this paper. 
\paragraph{Private Information Retrieval.} PIR has been used to facilitate anonymous communication in a variety of ways. The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.

\section{Measuring Anonymity}
  \textit{Anonymity sets}, introduced by Chaum in his Dining Cryptographers paper \cite{chaum-dc}, are widely used to analyze the anonymity provided by various p2p privacy schemes. Given a message and whatever information an attacker has obtained, the anonymity set for that message is the set of users who could have sent it. An anonymity set of size 1 means that the attacker knows exactly who sent the message.

This measure fails to capture some of the information gathered by the attacker. If, for instance, certain members of an anonymity set are more likely to have sent the message (which is never the case in Chaum's DC networks \cite{chaum-dc}), this information is not captured by the size of the anonymity set.

To solve this problem, Diaz \cite{Diaz02} and Serjantov \cite{Serj02} independently developed almost identical solutions. Their idea is this: given a message, consider the probability distribution of its senders. The entropy of this probability distribution then represents the number of bits an attacker still needs to obtain in order to identify the sender of the message.

Serjantov \cite{Serj02} calls this measure the \textit{size} $S$ of the anonymity probability distribution. Given $U$ is the set of all users, and $p_u$ is the probability that $u \in U$ sent the message under its probability distribution for users, then the $size$ of the probability distribution is:

\begin{center}
$ S = - \mathlarger{\sum}\limits_{u \in U} p_u $log$_2(p_u)$
\end{center}

For example, if we give one user a probability $1$ of sending the message, all other users have probability 0, and $S = -(1 * 0) = 0$, meaning the attacker needs no more information to identify the user.

\section{Privacy Goals}
  The goal of this system is to provide a method for communicating securely between parties through a central server with low latency and low communication overhead. We attempt to satisfy these requirements assuming the intermediate server may be compromised. By communicating securely we mean specifically (using terminology from \textbf{[6]}):
  \\\\\textbf{Communication Privacy}. Any party Eve cannot read the contents of intercepted messages sent between any two parties Alice and Bob. 
  \\\textbf{Participant Privacy}. This is also called \textbf{Unobservability} and \textbf{Untraceability}. Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants). The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
  \\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
\section{Central Server Communication}
 The majority of research into anonymous communication uses decentralized p2p networks. In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server. Many of the developed p2p techniques can be adapted by using a pseudo-p2p protocol, by having peers communicate with each other indirectly through the central server.

 In p2p protocols, delivering a message via a chain of peers or servers is common: Mix-based systems use cascades and mix networks, onion-based systems create circuits, etc. In this system we'll use the onion routing terminology and call the chain of peers a message passes through a $circuit$.

\begin{figure}[ht]
  \includegraphics[width=230px]{PSP.png}
  \caption{A simple pseudo-p2p circuit}
\end{figure}

@@

In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} . That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[TODO]]], as well (as we will discuss) by reordering and batching messages. 
\subsection{Adversaries}
In this context, we have several distinct types of adversaries we must consider:
\begin{enumerate}
  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
\end{enumerate}
\subsection{Security Flaws}
Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
\begin{enumerate}
\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ... P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$. This is because Surge knows that one of $A \cup \{P_1 ... P_n\}$ talked to Bob.
\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
\item\textbf{Timing.} Even if $P_1 ... P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking. 
\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
\end{enumerate}
This is fairly poor security. If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob. If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.

@@

If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations. The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose. If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$. Then, the $size$ of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.

In this way Surge gains no information about the sender of the message. If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate by randomly choosing the length of her circuit.

\subsection{The Palace} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$. If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$. The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.

@@

TODO: Apply PIR to obtain security guarantees even when $R \subset S$

\subsection{Peer Discovery}
Unfortunately, if peers discover eachother through Surge, he can ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).

This is a common problem in Onion routing schemes like Tor, as well as Mix networks. If directory servers collude with some routing servers, they can choose to only broadcast the existence of the compromised routing servers.

MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories. These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user. Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.

\subsection{Man in the Middle.} If both Alice and Bob are online, then they could use Diffie Hellman to ensure that Surge isn't acting as a Man in the middle. However, we'd like to allow offline delivery of messages.

This requires some form of web of trust, or some means of verifying public keys without trusting Surge.

\subsection{Peers as Mixes}
As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities. Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions. 
A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages. Common attacks are variants of the $n - 1$ or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.

@@

It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack. However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system. 
\section{Applying PIR}
\bibliography{paper.bib}
\bibliographystyle{plain}
\end{document}
